Actions Computed in the Milky Way are Not Invariant

### 2018-12-01 paper/ms.tex
Update README, fix paper
Test CI
Update pattern speed image
Test pattern speed image
Try bibtex
Update paper

@@

\title{Actions are Bad, Mmkay}

@@

In an axisymmetric potential the 6D phase space of stars' positions and
velocities can be reduced to a 3D space of invariant actions. For this reason
actions are commonly used to help interpret phase space. However, it is not
expected that actions are invariant in detail for the Milky Way --- it's
spiral arms, bar(s), and gas clouds are all non-axisymmetric features that
should induce long-term evolution in action space. However, these same
features will cause a star's true orbit to deviate slightly from its orbit in
an axisymmetric potential. If an observer assumes an axisymmetric potential
when computing actions, this will induce an artificial short-term phase
dependence of the actions, which we interpret as systematic error. Using the
potential of cosmological zoom-in simulations of Milky Way mass galaxies from
the FIRE collaboration (the Latte suite), we investigate the magnitude of
this systematic error. We find XXX. Something something lower limit.

@@

@@

Rockstar import in gizmo_analysis is commented out

@@

\appendix \section{Pattern Speed} Our estimation of the pattern speed is very
crude, but throughout the text we have adopted three different speeds in
order to demonstrate that qualitatively our results do not depend on the
precise numerical value of the pattern speed. We identify the spiral arms by
first plotting a $\phi$-$R$ 2D histogram, shown in
Figure~\ref{fig:pattern_speed}. In order to compute $\phi$ and $R$, we use the principal axes from \citep{2018arXiv180610564S}.

\begin{figure}
\includegraphics[width=\columnwidth]{{pattern_speed_by_eye}.png}
\caption{Pattern speed.}
\label{fig:pattern_speed}
\end{figure}

>>>>

\usepackage{graphicx}

@@

\title{Actions Computed in the Milky Way are Not Invariant}

@@

In an axisymmetric potential the 6D phase space of stars' positions and
velocities can be reduced to a 3D space of invariant actions. For this reason
actions are commonly used to help interpret phase space. We show that if one
assumes the wrong galactocentric reference frame this can induce artificial
non-axisymmetries which manifest as time dependence in the computed actions.
However, the Milky Way is not axisymmetric in detail and so there are no
truly axisymmetric axes. We instead define the  ``optimally axisymmetric''
axes as the reference frame which minimizes the time dependence of the
actions. Using cosmological zoom-in simulations from FIRE-2, we show that the
optimally axisymmetric reference frame can differ from standard methods of
calculating the galactocentric reference frame by (some numbers). We further
show that if one uses the conventional method to define the Galactic midplane
in this simulated galaxy, the midplane can vary by nearly a scale height
across the galaxy. This work calls into question the use of actions as
dynamical invariants unless these reference frame issues can be resolved.

% However, it is not expected that actions are invariant in detail for the
% Milky Way. This in-invariance can come about from assuming the wrong
% Galactic potential, but it can also come about due to true
% non-axisymmetries. We show that actions can gain artificial time-dependence
% also by assuming the wrong reference frame. We argue that standard methods
% for determining the galactocentric reference frame are not gu

% it's spiral arms, bar(s), and gas clouds are all non-axisymmetric features
% that should induce long-term evolution in action space. However, these same
% features will cause a star's true orbit to deviate slightly from its orbit
% in an axisymmetric potential. If an observer assumes an axisymmetric
% potential when computing actions, this will induce an artificial short-term
% phase dependence of the actions, which we interpret as systematic error.
% Using the potential of cosmological zoom-in simulations of Milky Way mass
% galaxies from the FIRE collaboration (the Latte suite), we investigate the
% magnitude of this systematic error. We find XXX. Something something lower
% limit.

@@

Midplane resolved with $\sim 370$ to $570$ star particles.

@@

Rockstar import in gizmo\_analysis is commented out

@@

\appendix \section{Pattern Speed} Our estimation of the pattern speed is very
crude, but throughout the text we have adopted three different speeds in
order to demonstrate that qualitatively our results do not depend on the
precise numerical value of the pattern speed. We identify the spiral arms by
first plotting a $\phi$-$R$ 2D histogram, shown in
Figure~\ref{fig:pattern_speed}. In order to compute $\phi$ and $R$, we use the principal axes from \citep{2018arXiv180610564S}. Push push

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{pattern_speed_by_eye}.png}
\caption{Pattern speed.}
\label{fig:pattern_speed}
\end{figure}
